\textbf{ Matching the forecast horizon with the relevant ecological processes }

### 2019-09-10 doc/manuscript.tex
Revisions to appendices

The compositional turnover affecting our focal species also influences total biomass, linking community and ecosystem dynamics. We repeated our focal species analysis 
for total community biomass, and the results were similar: the temporal model initially made the best forecasts immediately following the onset of the temperature
increase, but as the identity and abundances of species at the study site changed, the model weights rapidly shifted to the spatial model (Figs. \ref{fig:community-models-total} to \ref{fig:community-weights-total}).

@@

The temporal model, which we call $T$, starts with a time-series of ``observed" population sizes, or total biomasses, at one location, $N(t)$, for $t=1...n$ (the spatial index is suppressed because we only focus on one location at a time). In the community turnover example, we fit the following regression, which predicts biomass at time $t+1$ as a function of biomass ($N(t)$) and annual temperature ($K(t)$) at time $t$,
\begin{equation}
	\ln(N(t+1)) = T(N(t),K(t)) = \beta^T_0 +  \beta^T_1 ln(N(t)) +\beta^T_2 K(t)  +  \varepsilon
	\label{eqn:temporal_regression_community1}
\end{equation}
In the eco-evolutionary example, the response variable is the log of the population growth rate. The regression is 
\begin{equation}
	\ln(\frac{N(t+1)}{N(t)}) = T(N(t),K(t)) = \beta^T_0 +  \beta^T_1 ln(N(t)) +\beta^T_2 K(t)  +\beta^T_3 K(t)^2 +  \varepsilon
	\label{eqn:temporal_regression_ecoevo2}
\end{equation}
This version of the temporal model returns a per capita growth rate on the log scale. To predict population size at the next time step, we exponentiate the growth rate and multiply it by the current population size: $\exp(T(N(t),K(t))) N(t)$.

The combined model is a weighted average of predictions from the spatial and temporal models, with the weights changing as a function of time, here expressed as the forecast horizon. The weights change as a function of the square root of the forecast horizon, to allow rapid shifts in the model weights. 
\begin{equation}
logit(\omega_t)=\beta^C_0 + \beta^C_1 \sqrt{t}
\label{eqn:weights}
\end{equation}
For the community turnover example, the predicted biomass from the combined model is:
\begin{equation}
\hat{N}(t+1)= \omega \cdot T(N(t),K(t)) + (1-\omega) \cdot S(K(t)) 
\label{eqn:combined_model1}
\end{equation}
Again, we suppress the spatial subscript ($x$) here because we are focused on densities at just one location. For the eco-evolutionary example, the predicted population size from the combined model is:
\begin{equation}
	\hat{N}(t+1) = \omega \cdot exp(T(N(t),K(t))) N(t) + (1-\omega) \cdot S(K(t)) 
	\label{eqn:combined_model2}
\end{equation}

@@

The second step computes population growth, taking into account competition:
\begin{equation}
	N_{i}(x,t+1) = N'_{i}(x,t) + N'_{i}(x,t)[g_i(K(x) - Kmin_i) - c_i N'_{i}(x,t) - l_i \sum_{k} N'_{k}(x,t)]
\end{equation}
\comment{They have a delta t term right before the second P', but since this is a discrete time model and our time step always = 1, it seems confusing to add that...}
In the absence of competition, the growth rate ($g$) is determined by the difference between the temperature ($K$) at site $x$ and the focal species' minimum temperature tolerance, $Kmin$, the lowest temperature at which a species can maintain a positive growth rate. Growth is further reduced by intraspecific ($c$) and interspecific ($l$) competition. All species are assigned the same value of $c$, which represents the additional limitation each species experiences from intraspecific competition. This offset also stabilizes coexistence, since every species will exert stronger intra- than interspecific competition. However, values of $l$ vary among species to create a trade-off between growth rates and competitive ability and low temperature tolerance: fast-growing species (high $g$) are more tolerant of interspecific competition (low $l$) but are more limited by temperature (high $Kmin$).

@@

@@

\renewcommand{\thefigure}{C-\arabic{figure}}

\begin{figure}[tbp]
\centering
\includegraphics[width=0.7 \textwidth] {community_models_total.png}
\caption{(Results for total biomass from the community turnover model. Blue points show mean total biomass during the baseline period at locations across the temperature gradient, and the blue line shows predictions from the spatial model. Red points show annual total biomass during the baseline period as a function of annual temperature at the central site on the gradient. The red line shows predictions from the temporal model.   }
\label{fig:community-models-total}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=0.7 \textwidth] {community_forecast_total.png}
\caption{Results for total biomass from the community turnover model. (Top) Simulated annual temperatures (grey) and expected temperature (black), which was used to make forecasts, at the focal site. (Bottom) Simulated total biomass and forecasts from the spatial, temporal and combined models.  }
\label{fig:community-forecasts-total}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=0.7 \textwidth] {community_change_plus_weights_total.png}
\caption{Simulated changes in biomass of all species (grey) at the focal site in the metacommunity model, and the weight given to the temporal model for total biomass (blue). Year 0 in this figure corresponds to the start of the temperature increase. }
\label{fig:community-weights-total}
\end{figure}

>>>>

The compositional turnover affecting our focal species also influences total biomass, linking community and ecosystem dynamics. We repeated our focal species analysis for total community biomass, and the results were similar: the temporal model initially made the best forecasts immediately following the onset of the temperature increase, but as the identity and abundances of species at the study site changed, the model weights rapidly shifted to the spatial model (Figs. \ref{fig:community-models-total} and \ref{fig:community-forecasts-total}).

@@

The temporal model, which we call $T$, starts with a time-series of ``observed" population sizes, or total biomasses, at one location, $N(t)$, for $t=1...n$ (the spatial index is suppressed because we only focus on one location at a time). In the community turnover example, we fit the following regression, which predicts biomass at time $t+1$ as a function of biomass ($N(t)$) and annual temperature ($K(t)$) at time $t$,
\begin{equation}
\ln(N(t+1)) = T(N(t),K(t)) = \beta^T_0 +  \beta^T_1 \ln(N(t)) +\beta^T_2 K(t)  +  \varepsilon
\label{eqn:temporal_regression_community1}
\end{equation}
In the eco-evolutionary example, the response variable is the log of the population growth rate. The regression is 
\begin{equation}
\ln\left(\frac{N(t+1)}{N(t)}\right) = T(N(t),K(t)) = \beta^T_0 +  \beta^T_1 \ln(N(t)) +\beta^T_2 K(t)  +\beta^T_3 K(t)^2 +  \varepsilon
\label{eqn:temporal_regression_ecoevo2}
\end{equation}
This version of the temporal model returns a per capita growth rate on the log scale. To predict population size at the next time step, we exponentiate the growth rate and multiply it by the current population size: $\exp(T(N(t),K(t))) N(t)$.

The combined model is a weighted average of predictions from the spatial and temporal models, with the weights changing as a function of time, here expressed as the forecast horizon. The weights change as a function of the square root of the forecast horizon, to allow rapid shifts in the model weights. 
\begin{equation}
logit(\omega_t)=\beta^C_0 + \beta^C_1 \sqrt{t}
\label{eqn:weights}
\end{equation}
For the community turnover example, the predicted biomass from the combined model is:
\begin{equation}
\hat{N}(t+1)= \omega \cdot T(N(t),K(t)) + (1-\omega) \cdot S(K(t)) 
\label{eqn:combined_model1}
\end{equation}
Again, we suppress the spatial subscript ($x$) here because we are focused on densities at just one location. For the eco-evolutionary example, the predicted population size from the combined model is:
\begin{equation}
\hat{N}(t+1) = \omega \cdot \exp(T(N(t),K(t))) N(t) + (1-\omega) \cdot S(K(t)) 
\label{eqn:combined_model2}
\end{equation}

@@

The second step computes population growth, taking into account competition:
\begin{equation}
N_{i}(x,t+1) = N'_{i}(x,t) + N'_{i}(x,t)[g_i(K(x) - Kmin_i) - c_i N'_{i}(x,t) - l_i \sum_{k} N'_{k}(x,t)]
\end{equation}
In the absence of competition, the growth rate ($g_i$) is determined by the difference between the temperature at site $x$ ($K(x)$) and the focal species' minimum temperature tolerance, $Kmin_i$, the lowest temperature at which a species can maintain a positive growth rate. Growth is further reduced by intraspecific and interspecific competition, parameterized by $c_i$ and $l_i$.  All species are assigned the same value of $c_i$, which represents an additional effect of intraspecific competition on top of interspecific competition. This stabilizes coexistence, since every species will exert stronger intra- than interspecific competition. However, values of $l$ vary among species to create a trade-off between growth rates and competitive ability versus low temperature tolerance: fast-growing species (high $g_i$) are more tolerant of interspecific competition (low $l_i$) but are more limited by temperature (high $Kmin_i$).

@@

\newpage

@@

\renewcommand{\thefigure}{S-\arabic{figure}}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.7 \textwidth] {community_models_total.png}
\caption{(Results for total biomass from the community turnover model. Blue points show mean total biomass during the baseline period at locations across the temperature gradient, and the blue line shows predictions from the spatial model. Red points show annual total biomass during the baseline period as a function of annual temperature at the central site on the gradient. The red line shows predictions from the temporal model.   }
\label{fig:community-models-total}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[width=0.7 \textwidth] {community_forecast_total.png}
\caption{Results for total biomass from the community turnover model. (A) Simulated annual temperatures (grey) and expected temperature (black), which was used to make forecasts, at the focal site. (B) Simulated total biomass and forecasts from the spatial, temporal and combined models. (C) Simulated changes in biomass of all species (grey) at the focal site in the metacommunity model, and the weight given to the temporal model for total biomass (blue). Year 1000 in this figure corresponds to the start of the temperature increase.  }
\label{fig:community-forecasts-total}
\end{figure}
